\documentclass[a4paper,11pt]{article}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{cfr-lm}
\usepackage{lipsum}
\usepackage{marvosym}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[most]{tcolorbox}
\usepackage{setspace}

% Adjust the width of vertical lines in the table
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\renewcommand\tabularxcolumn[1]{m{#1}}

\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\normalfont\bfseries}
{}
{0em}
{}[\vspace{-0.6em}] % Adjust the spacing here

\begin{document}
\pagestyle{empty} % Removes page numbers

\vspace{-10mm}
\begin{center}
    {\Huge\scshape Kanak Tanwar}
    
    \vspace{0.01em}
    \faGlobe\ \href{https://kanaktanwar.tech}{kanaktanwar.tech} $\vert$
    \faGithub\ \href{https://github.com/kanakOS01}{github.com/kanakOS01} $\vert$
    
    \faEnvelope\ \href{mailto:kanaktanwarpro@gmail.com}{kanaktanwarpro@gmail.com} $\vert$
    \faLinkedin\ \href{https://www.linkedin.com/in/kanak-tanwar/}{linkedin.com/in/kanak-tanwar}
\end{center} 
\vspace{-7mm}

    \small\begin{tabularx}{\textwidth}{|c|Y|c|c|}
    \end{tabularx}

\section*{Experience}
\vspace{-2mm}

\subsection{Backend Intern | Vetic, Gurgaon, India
\hfill April 2025 to Present}
\begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Implemented a task scheduler using Redis for timed job execution as part of onboarding.
    \item Solved various backend tasks involving FastAPI and Django, contributing to live production systems.
    \item Fixed reported bugs and implemented new features based on given requirements.
\end{itemize}
\vspace{-3mm}


\subsection{AI Intern | Mentorpal.ai 
\hfill June 2024 to July 2024}
\begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Engineered an extension to suggest personalized messages to prospective leads on LinkedIn.
    \item Developed an internal tool to allow QA with various resume using LangChain and LLM improving efficiency of the team.
    \item Scraped various websites using Selenium and BeautifulSoup to provide client leads.
    \item Collaborated with a team of professionals to design, develop, and implement innovative solutions driving the company’s growth.
\end{itemize}
\vspace{-5mm}

\section*{Projects}
\vspace{-2mm}
\subsection*{\href{https://github.com/kanakOS01/git-chat}{Git Chat}}
\begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Developed a RAG-based application enabling Q/A interactions with GitHub repositories.
    \item Utilized Weaviate vector database and LangChain for efficient data management and processing and built a user-friendly UI on Streamlit to facilitate seamless user interaction.
    \item Implemented functionality to automatically load new repositories when encountered, ensuring up-to-date data access.
\end{itemize}
\vspace{-3mm}

\subsection*{\href{https://github.com/kanakOS01/social-media-fastapi}{Social Media API}}
\begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Programmed a robust API using FastAPI for CRUD operations, authentication, and schema validation.
    \item Integrated PostgreSQL with SQLAlchemy for seamless database management and utilized Alembic for migrations.
    \item Deployed the API to an Ubuntu machine on DigitalOcean, configured a domain name, and implemented an SSL certificate for secure access.
    \item Implemented a CI/CD pipeline using GitHub Actions for streamlined deployment and updates.
\end{itemize}
\vspace{-3mm}

\subsection*{\href{https://github.com/kanakOS01/movie-recommender-system}{Movie Recommendation System}}
\begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Cleaned and transformed TMDB dataset from Kaggle with about 5000 data points.
    \item Utilized text processing techniques such as converting text to vectors using bag-of-words model and text vectorization to improve performance. 
    \item Built and fine-tuned a content-based recommendation system using sklearn to recommend movies similar to the input.
\end{itemize}
\vspace{-3mm}

% \subsection*{\href{https://github.com/kanakOS01/house-prediction-model}{House Price Prediction Project}}
% \begin{itemize}[itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
%     \item Processed a Bangalore housing dataset comprising more than 13,000 data points.
%     \item Engineered a linear regression model using scikit-learn to predict house prices based on the Bangalore House Price Data from Kaggle, achieving an 85\% accuracy rate.
%     \item Designed a user-friendly website using HTML, CSS, JS, Flask and deployed the website on an AWS EC2 instance using NGINX reverse proxy.
% \end{itemize}
% \vspace{-5mm}

\section{Education}
\vspace{-2mm}
    \setlength{\tabcolsep}{2pt} % Adjust the spacing between columns in the table
    \small\begin{tabularx}{\textwidth}{|c|Y|c|c|}
      \hline
      \textbf{Degree/Certificate} & \textbf{Institute/Board} & \textbf{CGPA/Percentage} & \textbf{Graduation Date}\\
      \hline
      B.Tech - CSE & Dronacharya College Of Engineering & 86\% & Ongoing\\
      \hline
      Senior Secondary & Manav Rachna International School & 96.0\% & May 2022 \\
      \hline
      Secondary & Manav Rachna International School & 97.6\% & May 2020 \\
      \hline
    \end{tabularx}
\vspace{-5mm}

\section*{Skills}
\vspace{-2mm}
\begin{itemize}[label=\textbullet, left=0pt]
    \item \textbf{Programming Languages -} \small Python, Java, C/C++, JavaScript, R, Bash
    \vspace{-2mm}
    \item \textbf{Web Development -} \small HTML, CSS, JS, Bootstrap, Flask, FastAPI, Django
    \vspace{-2mm}
    \item \textbf{Data Science and Machine Learning -} \small NumPy, Pandas, Matplotlib, Scikit Learn, LangChain
    \vspace{-2mm}
    \item \textbf{Database and ORM -} \small MySQL, MongoDB, PostgreSQL, SQLAlechemy, Beanie
    \vspace{-2mm}
    \item \textbf{Misc -} \small Git, Linux, AWS, Streamlit, Docker, BeautifulSoup, Selenium, Fabric
    \vspace{-2mm}
\end{itemize}
\vspace{-5mm}

\section*{Achievements}
\vspace{-2mm}
\begin{itemize}[label=\textbullet, left=0pt, itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Gate qualified DA (AIR 702) and CS (AIR 3050).
    \item Regionalist at ICPC Amritapuri, 2023.
    \item AIML track prize winner in HackKRMU 3.0 (WanderAI Project).
    \item AIR 8 in NCAT 2023.
\end{itemize}
\vspace{-5mm}

\section*{Key Courses}
\vspace{-2mm}
\begin{itemize}[label=\textbullet, left=0pt, itemsep=0pt,parsep=0pt,topsep=0pt,partopsep=0pt]
    \item Database Management with SQL, AIML fundamentals, Advanced Data Structures, Object Oriented Programming, Operating Systems
    \item Mathematics: Linear Algebra, Probability \& Statistics, Basic Calculus
\end{itemize}
\vspace{-3mm}

\end{document}
